analysis-pilot

### 2023-08-18 code/analysis-pilot.Rmd
labels on graphs

ggplot(data = accuracy, aes(x = percent, y = reorder(game, -percent))) +
  geom_bar(stat = "identity", position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  theme_classic() +
  xlab("\nPercentage Accuracy") +
  ylab("Game ID\n") +
  scale_x_continuous(breaks=seq(0,100,10), expand=c(0,0)) +
  theme(aspect.ratio = 4/5,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.position = "none")
ggsave("AccuracySorted.png")

@@

ggplot(data = accuracy, aes(x = image, y = percent)) +
  geom_bar(stat = "identity", position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  geom_smooth(method="lm")+
  #geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  theme_classic() +
  xlab("\nTarget") +
  ylab("Percent accuracy\n") +
  #scale_x_continuous(breaks=seq(1,12,1)) +
  scale_y_continuous(breaks=seq(0,100,10), limits = c(0, 100), expand=c(0,0)) +
  theme(aspect.ratio = 4/5,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.position = "none")
ggsave("AccuracybyTarget.png")
```

>>>>

ggplot(data = accuracy, aes(x = percent, y = reorder(game, -percent))) +
  geom_bar(stat = "identity", position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  theme_classic() +
  xlab("\nPercentage accuracy") +
  ylab("Game ID\n") +
  scale_x_continuous(breaks=seq(0,100,10), expand=c(0,0)) +
  theme(aspect.ratio = 4/5,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.position = "none")
ggsave("AccuracySorted.png")

@@

ggplot(data = accuracy, aes(x = image, y = percent)) +
  geom_bar(stat = "identity", position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  geom_smooth(method="lm")+
  theme_classic() +
  xlab("\nTarget") +
  ylab("Percent accuracy\n") +
  #scale_x_continuous(breaks=seq(1,12,1)) +
  scale_y_continuous(breaks=seq(0,100,10), limits = c(0, 100), expand=c(0,0)) +
  geom_text(aes(label = percent), vjust = 1.7, color = "white", size = 3) +
  theme(aspect.ratio = 4/5,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.position = "none")
ggsave("AccuracybyTarget.png")
```
